% FIXTURE: sample_clean
% EXPECTED: 100/100  — no failures, no warnings
% PURPOSE:  Baseline. Verifies the checker does not false-positive on a well-formed resume.
\documentclass[10pt, letterpaper]{article}
\usepackage[top=1.5cm, bottom=1.5cm, left=1.5cm, right=1.5cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}

% ATS unicode hints — required for pass on parse.unicode_mapping
\input{glyphtounicode}
\pdfgentounicode=1

\pagestyle{empty}
\setlength{\parindent}{0pt}

\begin{document}

% ── Contact ──────────────────────────────────────────────────────────
\begin{center}
    {\Large \textbf{Jane Doe}}\\[4pt]
    Toronto, ON \quad|\quad
    \href{mailto:jane@example.com}{jane@example.com} \quad|\quad
    +1 416-555-0100 \quad|\quad
    \href{https://linkedin.com/in/janedoe}{linkedin.com/in/janedoe} \quad|\quad
    \href{https://github.com/janedoe}{github.com/janedoe}
\end{center}

% ── Summary ──────────────────────────────────────────────────────────
\section*{Summary}
Software engineer with 5 years of experience building scalable Python web services, REST APIs,
and machine learning pipelines. Skilled in Docker, AWS, PostgreSQL, and CI/CD automation.

% ── Technical Skills ─────────────────────────────────────────────────
\section*{Technical Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Languages:} Python, JavaScript, SQL
    \item \textbf{Frameworks:} FastAPI, Flask, React
    \item \textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions
    \item \textbf{Databases:} PostgreSQL, MongoDB, MySQL
    \item \textbf{ML:} scikit-learn, PyTorch, model deployment, LLMs, RAG, LangChain
\end{itemize}

% ── Professional Experience ───────────────────────────────────────────
\section*{Professional Experience}

\textbf{Senior Software Engineer}, Acme Corp \hfill Jan 2021 -- Present\\
Toronto, ON
\begin{itemize}[leftmargin=*]
    \item Designed and deployed REST APIs serving 2M requests/day using FastAPI and PostgreSQL.
    \item Reduced infrastructure costs by 30\% by migrating batch jobs to AWS Lambda with Docker.
    \item Built a RAG-based document search system using LangChain and semantic search, cutting
          retrieval latency by 60\%.
\end{itemize}

\vspace{4pt}
\textbf{Software Engineer}, Beta Inc \hfill Jun 2018 -- Dec 2020\\
Vancouver, BC
\begin{itemize}[leftmargin=*]
    \item Developed Python microservices for an IoT data pipeline processing 50K events/minute.
    \item Implemented CI/CD pipelines with GitHub Actions, reducing release cycle from 2 weeks to 2 days.
    \item Led migration from MySQL to PostgreSQL, improving query performance by 40\%.
\end{itemize}

% ── Education ────────────────────────────────────────────────────────
\section*{Education}
\textbf{BSc Computer Science}, University of Toronto \hfill Sep 2014 -- Jun 2018

% ── Projects ─────────────────────────────────────────────────────────
\section*{Projects}

\textbf{ML Pipeline Toolkit} \hfill \href{https://github.com/janedoe/ml-toolkit}{github.com/janedoe/ml-toolkit}
\begin{itemize}[leftmargin=*]
    \item Open-source Python library for model deployment and monitoring; 500+ GitHub stars.
    \item Supports LLMs, RAG workflows, and AWS SageMaker integration out of the box.
\end{itemize}

\end{document}
