% FIXTURE: sample_table_skills_fontawesome
% EXPECTED WARNINGS  : layout.package.fontawesome5, layout.package.tabularx
% PURPOSE: Uses fontawesome5 for contact icons (glyphs may not extract) and
%          tabularx to lay out the skills section as a grid (reading-order risk).
\documentclass[10pt, letterpaper]{article}
\usepackage[top=1.5cm, bottom=1.5cm, left=1.5cm, right=1.5cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fontawesome5}   % INTENTIONAL ISSUE → layout.package.fontawesome5 WARN
\usepackage{tabularx}       % INTENTIONAL ISSUE → layout.package.tabularx WARN

\input{glyphtounicode}
\pdfgentounicode=1

\pagestyle{empty}
\setlength{\parindent}{0pt}

\begin{document}

% ── Contact (icons from fontawesome5 precede plain-text links) ────────
\begin{center}
    {\Large \textbf{Carlos Rivera}}\\[6pt]
    \faEnvelope\ \href{mailto:carlos@example.com}{carlos@example.com} \quad
    \faPhone\ +1 780-555-0144 \quad
    \faLinkedin\ \href{https://linkedin.com/in/carlosrivera}{linkedin.com/in/carlosrivera} \quad
    \faGithub\ \href{https://github.com/carlosrivera}{github.com/carlosrivera}
\end{center}

\section*{Summary}
Data engineer with 6 years of experience designing ETL pipelines, data warehouses, and
ML feature stores. Strong background in Python, Spark, AWS, and PostgreSQL.

% ── Skills (tabularx grid) ────────────────────────────────────────────
% INTENTIONAL ISSUE: skill grid in tabularx → layout.package.tabularx WARN
\section*{Technical Skills}
\begin{tabularx}{\linewidth}{X X X}
    Python        & Apache Spark  & AWS Redshift  \\
    PostgreSQL    & Docker        & Kubernetes    \\
    LLMs          & RAG           & LangChain     \\
    FastAPI       & CI/CD         & Airflow       \\
\end{tabularx}

\section*{Professional Experience}
\textbf{Senior Data Engineer}, DataCo \hfill Apr 2019 -- Present\\
Edmonton, AB
\begin{itemize}[leftmargin=*]
    \item Designed Spark-based ETL pipelines processing 5TB/day into AWS Redshift.
    \item Built a RAG-powered data catalogue using LangChain, LLMs, and semantic search.
    \item Containerised all services with Docker and automated deployments via CI/CD and Kubernetes.
\end{itemize}

\textbf{Data Engineer}, Analytics Ltd \hfill Aug 2016 -- Mar 2019
\begin{itemize}[leftmargin=*]
    \item Migrated legacy MySQL pipelines to PostgreSQL, reducing query latency by 45\%.
    \item Developed Python libraries for data validation used across 5 teams.
\end{itemize}

\section*{Education}
\textbf{MSc Data Science}, University of Alberta \hfill Sep 2014 -- Jun 2016

\section*{Projects}
\textbf{StreamFlow} — Real-time IoT event processor built with Python, Kafka, and AWS.
\begin{itemize}[leftmargin=*]
    \item Ingests 200K events/minute; powers dashboards for model deployment monitoring.
\end{itemize}

\end{document}
